New storyline for 3rd version:

Main changes:
- Take perspective of decision maker, present engineering problem: How safe should a structure be, and why do we need a societal/environmental perspective? -> aggregation within utilitarianism
- Add `population' of H-K structures

Main question: Where to reflect on ethics within storyline?
- In introduction
- Right after introduction
- While introducing current approach
- After that (as in 2nd draft)

- Section 1 Introduction:
    Perspective of decision-makers!
    S-LCA ref naar eerste paper
    Present problem from engineering perspective. Why do we need sustainability?
    No cost functions here yet
    Ethical theories here or later? As separate section or within introduction?

- Section 2 Status quo

- Section 3 on ethics (ethisch kader)
    Kosten meenemen in utilitarian (optimalisatie) approach:
    Kosten levens: BNP, verschil per persoon

Eind sectie 3: welk probleem gaan we oplossen, en waarom (in sectie 3).


- Section 4: Approach
    Koppeling met decision probleem, waarom (nog steeds) optimalisatie? Passen de principes van hiervoor daar in?
    Eisen gesteld vanuit ethisch perspectief, met deze method gaan we daar aan voldoen.
    Acceptability als ondergrens: reductie bbp <-> veiligheid, voelt een gebruiker dat wel? Cx en G op maatchappijniveau, doen we voor consistency maar speelt wel rol vanuit ethisch oogpunt. Reflecteren, maar wel gebruiken want anders zet je de waarde impliciet op 0. Moet een vorm van MLSC,SWTP,SVSL etc hebben
    Reflect C\_H back to ethics. What does it mean for decision-maker? For society? Even without just the equation?
    Present both cost functions here
    Present optimisations: weighted sum, epsilon constraint
- Case study
    Keep as-is, shorten where possible but keep readable
    Mention 'population' here already? Maybe also other parameters for next section.
    State goal of generalisability.
- Analysis
    Add population of HK-filtered designs
    More readable plot for CoV's, focus on delta beta
    Ratio ce/steel ook bekijken, 0.4 tot 1 -> gaat de delta beta wel beinvloeden
- Conclusion
    Reflect results back on ethics: larger failure probability, environmental damage vs safety
    Push-pull effect
    Generalisability of case study, state delta beta range that will likely hold for similar structures
    ce / csteel
    Diff discount mention? (p3)
    Reflecteren op ethics!!

    
    
    
    










% - Introduction
% - Status Quo / State-of-the-art
%     Only optimal!
%     General description
% - Need for improvement / appraisal
%     Reframe into ethical considerations: human lives, sustainability
%     $C_H$ discussion here here
%     `Burden' of emissions
% - Proposed improvement
%     Present as multi-objective problem here
%     Shadow-costing
% - Case study
%     Skip description as much as possible
%     Maybe derive values for $C_1$ etc. directly?
% - Analysis
%     Keep beta slide, other figures if interesting
%     Explain based on multi-objective interpr.
% - Conclusion
%     Difference in beta
%     Effect of different criteria
%     Reflect on ethics
%     Maybe present discounting as future topic? Would connect to P1 review

% Try to keep length < 6000 words